---
title: "beta_gen"
author: "Toshiki Tsuda (toshiki.tsuda@yale.edu), Yanchun Jin (chnjyc@gmail.com), Ryo Okui (okuiryo@e.u-tokyo.ac.jp)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{beta_gen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(rmarkdown.html_vignette.check_title = FALSE) 
```

## Functions

The **mteucb** provides four functions as below:

-  `p_hut_gen()`: Estimation of  propensity score thourgh maximum likelihood estimation.
-  `beta_hut_gen()`: Estimation of  finite parameters by partially linear estimation.
-  `unif_gen()`: Computation of uniform confidence bands for an MTE function given the parametric part of MTE is known. 
-  `uniform_con_gen()`: Computation of uniform confidence bands for an MTE function given data.

In this page, we introduce how to use `beta_hut_gen()` for obtaining finite dimensional parameters of an MTE function.

#### Arguments

-  `outcome_name`: The name of the outcome
-  `covariate_name`: The name of covariate
-  `instrument_name`: The name of instrument variables
-  `treatment_name`: The name of a treatment variable
-  `data`: data.frame to be used for the estimation of MTE
-  `family`: The distribution used for the calculation of the propensity score.
You can choose "probit" or "logit". The default choice is "probit".
-  `trim`: To mitigate the effect of ill behavior of estimtaed propensity scores,
we set those less than the value of trim or larger than (1-the value of trim) as the value of the value of trim  or (1-the value of trim).
-  `intercept`: 'TRUE' or 'FLASE' option to decide whether you include an intercept
for estimating the propensity score or not. The default choice is 'TRUE'.
-  `se_type`: The sort of standard error sought. The options are "HC0", "HC1" (or "stata", the equivalent) , "HC2" (default), "HC3", or "classical".

#### Returns
`beta_gen()` returns a list that contains the following two elements:

- `Beta`: Finite parameters of an MTE function estimated by partially linear estimation

- `SE`: The standard error of estimated parameters


## Example

First, we generate the data used for the estimation of MTE, icluding outcome, covariates, instruments, and tretament.

```{r, eval = T, echo = T}
# Load the package
library(mteucb)
library(MASS)
# Generate artificial data
#: The number of cross-sectional units
# tau: The length of time series
# continuous: Generate a continuous (resp. discrete) covariate if it is TRUE (resp. FALSE).
set.seed(1)

#Generate covariates and instruments with sample size 2000.
SS<-2000
X1<-rnorm(n=SS,mean=0,sd=1)
X2<-rnorm(n=SS,mean=0,sd=1)
X3<-rnorm(n=SS,mean=0,sd=1)
X4<-rnorm(n=SS,mean=0,sd=1)
Z1<-rnorm(n=SS,mean=0,sd=1)
Z2<-rnorm(n=SS,mean=0,sd=1)
Z3<-rnorm(n=SS,mean=0,sd=1)
Z4<-rnorm(n=SS,mean=0,sd=1)

#Generate unobserved heterogeneity and errors to generate outcome and treatment
E0<-c(1,0.5,0.3)
E1<-c(0.5,1,0.8)
E2<-c(0.3,0.8,1)
E<-cbind(E0,E1,E2)
E4<-mvrnorm(n=SS,mu=c(0,0,0),Sigma=E)
U0<-E4[,1]
U1<-E4[,2]
V<-E4[,3]
Expl<-cbind(X1,X2,X3,X4)
Instr<-cbind(X1,X2,X3,X4,Z1,Z2,Z3,Z4)
PInstr<-cbind(Z1,Z2,Z3,Z4)

#Define parameters.
beta0<-c(0.5,0.1,-0.1,-0.5)
beta1<-c(0.8,0.4,-0.4,-0.8)
ganma0<-c(0.4,0.4,0.4,0.4,0.3,0.3,0.3,0.3)

#Generate outcome and treatment
D<-numeric(SS)
for(i in 1:SS){
  if ((ganma0 %*% (Instr[i,]))>V[i]){
    D[i]=1}
}
Y<-numeric(SS)
for(i in 1:SS){
  Y[i]<-D[i]*((beta1%*%Expl[i,])+U1[i])+(1-D[i])*((beta0%*%Expl[i,])+U0[i])
}
demo=as.data.frame(cbind(Y,Expl,PInstr,D))
```

We can check the generated variable by using `head()`.

```{r, eval = T, echo = T}
head(demo)
```

By using `beta_gen()`, we obtain finite parameters of a MTE function with standard error.
```{r, eval = T, echo = T}
RESULT_Beta<-beta_gen(outcome_name="Y",
                      covariate_name=c("X1","X2","X3","X4"),
                      instrument_name=c("Z1","Z2","Z3","Z4"),
                      treatment_name= "D",
                      data=demo,
                      family="probit",
                      trim=0.01,
                      intercept=TRUE,
                      se_type="HC2"
)

head(RESULT_Beta$Beta)
head(RESULT_Beta$SE)

```

## Note

-


## Reference

- Carneiro and Lee (2009). Estimating distributions of potential outcomes using local instrumental variables with an application to changes in college enrollment and wage inequality. Journal of Econometrics, 2009, vol. 149, issue 2, 191-208

-  Tsuda, T, Jin, Y., & Okui, R. (2024+).
Uniform Confidence Band for Marginal Treatment Effect Function.
will be available on arXiv.
