---
title: "p_hut_gen (under construction)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{p_hut_gen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE) 
```

## Functions

The **mteucb** provides four functions as below:

-  `p_hut_gen()`: Estimation of  propensity score thourgh maximum likelihood estimation.
-  `beta_hut_gen()`: Estimation of  finite parameters by partially linear estimation.
-  `p_hut_gen()`:
-  `p_hut_gen()`:

In this page, we introduce how to use `p_hut_gen()` for obtaining the estimated propensity score. 

#### Arguments

-  `outcome_name`: The name of the outcome
-  `covariate_name`: The name of covariate
-  `instrument_name`: The name of instrument variables
-  `treatment_name`: The name of a treatment variable
-  `data`: data.frame to be used for the estimation of MTE
-  `family`: The distribution used for the calculation of the propensity score.
You can choose "probit" or "logit". The default choice is "probit".
-  `trim`: To mitigate the effect of ill behavior of estimtaed propensity scores,
we set those less than the value of trim or larger than (1-the value of trim) as the value of the value of trim  or (1-the value of trim).
-  `intercept`: 'TRUE' or 'FLASE' option to decide whether you include an intercept
for estimating the propensity score or not. The default choice is 'TRUE'.

#### Returns
`p_hut_gen()` returns a list that contains the following three elements:

- `Data`: A data frame equipped with the estimated propensity score. 

- `SampleSize`: The number of data used to estimate the propensity score. 

- `P_hut`: A data frame that only includes the estimated propensity score.

## Example

First, we generate the data used for the estimation of MTE, icluding outcome, covariates, instruments, and tretament.

```{r, eval = T, echo = T}
# Load the package
library(mteucb)
library(MASS)

# Generate artificial data
#: The number of cross-sectional units
# tau: The length of time series
# continuous: Generate a continuous (resp. discrete) covariate if it is TRUE (resp. FALSE).
set.seed(1)

#Generate covariates and instruments with sample size 2000.
SS<-2000
X1<-rnorm(n=SS,mean=0,sd=1)
X2<-rnorm(n=SS,mean=0,sd=1)
X3<-rnorm(n=SS,mean=0,sd=1)
X4<-rnorm(n=SS,mean=0,sd=1)
Z1<-rnorm(n=SS,mean=0,sd=1)
Z2<-rnorm(n=SS,mean=0,sd=1)
Z3<-rnorm(n=SS,mean=0,sd=1)
Z4<-rnorm(n=SS,mean=0,sd=1)

#Generate unobserved heterogeneity and errors to generate outcome and treatment
E0<-c(1,0.5,0.3)
E1<-c(0.5,1,0.8)
E2<-c(0.3,0.8,1)
E<-cbind(E0,E1,E2)
E4<-mvrnorm(n=SS,mu=c(0,0,0),Sigma=E)
U0<-E4[,1]
U1<-E4[,2]
V<-E4[,3]
Expl<-cbind(X1,X2,X3,X4)
Instr<-cbind(X1,X2,X3,X4,Z1,Z2,Z3,Z4)
PInstr<-cbind(Z1,Z2,Z3,Z4)

#Define parameters.
beta0<-c(0.5,0.1,-0.1,-0.5)
beta1<-c(0.8,0.4,-0.4,-0.8)
ganma0<-c(0.4,0.4,0.4,0.4,0.3,0.3,0.3,0.3)

#Generate outcome and treatment
D<-numeric(SS)
for(i in 1:SS){
  if ((ganma0 %*% (Instr[i,]))>V[i]){
    D[i]=1}
}
Y<-numeric(SS)
for(i in 1:SS){
  Y[i]<-D[i]*((beta1%*%Expl[i,])+U1[i])+(1-D[i])*((beta0%*%Expl[i,])+U0[i])
}
demo=as.data.frame(cbind(Y,Expl,PInstr,D))
```

We can check the generated variable by using `head()`.

```{r, eval = T, echo = T}
head(demo)
```

By using `p_hut_gen()`, we obtain a dataframe with the estimated propensity score.
```{r, eval = T, echo = T}
RESULT_P_hut<-p_hut_gen(outcome_name="Y",
                                 covariate_name=c("X1","X2","X3","X4"),
                                 instrument_name=c("Z1","Z2","Z3","Z4"),
                                 treatment_name= "D",
                                 data=demo,
                                 family="probit", 
                                 trim=0.01, #
                                 intercept=TRUE
                                )
head(RESULT_P_hut$Data)
head(RESULT_P_hut$SampleSize)
head(RESULT_P_hut$P_hut)


```

## Note
