---
title: "unif_gen"
author: "Toshiki Tsuda (toshiki.tsuda@yale.edu), Yanchun Jin (chnjyc@gmail.com), Ryo Okui (okuiryo@e.u-tokyo.ac.jp)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{unif_gen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7.5, 
  fig.height = 5 
)

options(rmarkdown.html_vignette.check_title = FALSE) 
```

## Functions

The **mteucb** provides four functions as below:

-  `p_hut_gen()`: Estimation of  propensity score thourgh maximum likelihood estimation.
-  `beta_hut_gen()`: Estimation of  finite parameters by partially linear estimation.
-  `unif_gen()`: Computation of uniform confidence bands for an MTE function given the parametric part of MTE is known. 
-  `uniform_con_gen()`: Computation of uniform confidence bands for an MTE function given data.

In this page, we introduce how to use `unif_gen()` for obtaining a confidence band of an MTE function given data with estimated propensity score and estimated finite parameters.

#### Arguments

-  `outcome_name`: The name of the outcome
-  `covariate_name`: The name of covariate
-  `instrument_name`: The name of instrument variables
-  `treatment_name`: The name of a treatment variable
-  `P_hut_name`: The name of estimated propensity scores.
-  `beta0`: A vector of parameters of a linear model for the outcome given an individual is not treated
-  `beta1`: A vector of parameters of a linear model for the outcome given an individual is treated
-  `data`: data.frame including propensity scores to be used for the estimation of MTE
-  `bw`: 	The bandwidth used in estimating the nonparametric part of MTE
-  `l_eval`: 	The minimum value of evaluation points for the estimated MTE
-  `u_eval`: 	The maximum value of evaluation points for the estimated MTE
-  `kernel`: The kernel function used in estimating the nonparametric part of MTE. You can choose 'gaussK' (gaussian kernel), and 'EapK' (Epanechinikov kernel). The default choice is 'gaussK'.
-  `covariate_value`: A covariate value to plot the estimate MTE
-  `significance_level`: The significance level for the construction of uniform confidence band

#### Returns
`unif_gen()` returns a list that contains the following two elements:

- `Estimation`: A data frame of the following results: outcome, covariate, instrument variables, treatment and propensity score ranging from $0.05*\lceil \text{l_eval}/0.05\rceil$ to $0.05*\lfloor \text{u_eval}/0.05\rfloor$ with width $0.05$.

- `Plot`: A list that contains the ggplot elements for unifrom confidence band


## Example

First, we generate the data used for the estimation of MTE, icluding outcome, covariates, instruments, and tretament.

```{r, eval = T, echo = T}
# Load the package
library(mteucb)
library(MASS)

# Generate artificial data
#: The number of cross-sectional units
# tau: The length of time series
# continuous: Generate a continuous (resp. discrete) covariate if it is TRUE (resp. FALSE).
set.seed(1)

#Generate covariates and instruments with sample size 2000.
SS<-2000
X1<-rnorm(n=SS,mean=0,sd=1)
X2<-rnorm(n=SS,mean=0,sd=1)
X3<-rnorm(n=SS,mean=0,sd=1)
X4<-rnorm(n=SS,mean=0,sd=1)
Z1<-rnorm(n=SS,mean=0,sd=1)
Z2<-rnorm(n=SS,mean=0,sd=1)
Z3<-rnorm(n=SS,mean=0,sd=1)
Z4<-rnorm(n=SS,mean=0,sd=1)

#Generate unobserved heterogeneity and errors to generate outcome and treatment
E0<-c(1,0.5,0.3)
E1<-c(0.5,1,0.8)
E2<-c(0.3,0.8,1)
E<-cbind(E0,E1,E2)
E4<-mvrnorm(n=SS,mu=c(0,0,0),Sigma=E)
U0<-E4[,1]
U1<-E4[,2]
V<-E4[,3]
Expl<-cbind(X1,X2,X3,X4)
Instr<-cbind(X1,X2,X3,X4,Z1,Z2,Z3,Z4)
PInstr<-cbind(Z1,Z2,Z3,Z4)

#Define parameters.
beta0<-c(0.5,0.1,-0.1,-0.5)
beta1<-c(0.8,0.4,-0.4,-0.8)
ganma0<-c(0.4,0.4,0.4,0.4,0.3,0.3,0.3,0.3)

#Generate outcome and treatment
D<-numeric(SS)
for(i in 1:SS){
  if ((ganma0 %*% (Instr[i,]))>V[i]){
    D[i]=1}
}
Y<-numeric(SS)
for(i in 1:SS){
  Y[i]<-D[i]*((beta1%*%Expl[i,])+U1[i])+(1-D[i])*((beta0%*%Expl[i,])+U0[i])
}
demo=as.data.frame(cbind(Y,Expl,PInstr,D))
```

We can check the generated variable by using `head()`.

```{r, eval = T, echo = T}
head(demo)
```

To generate a confidence band, we set some parameters

```{r, eval = T, echo = T}
Supp_P_hut_U<-0.85
Supp_P_hut_L<-0.15
O_SS<-1000
B2<-seq(Supp_P_hut_L,Supp_P_hut_U,length=O_SS)
covariate_value<-c(0,0,0,0)
```

By using `unif_gen()`, we obtain a confidence band of a MTE function.
```{r, eval = T, echo = T}
RESULT_P_hut<-p_hut_gen(outcome_name="Y",
                        covariate_name=c("X1","X2","X3","X4"),
                        instrument_name=c("Z1","Z2","Z3","Z4"),
                        treatment_name= "D",
                        data=demo,
                        family="probit",
                        trim=0.01,
                        intercept=TRUE
)

RESULT_unif<-unif_gen(outcome_name="Y",
                      covariate_name=c("X1","X2","X3","X4"),
                      instrument_name=c("Z1","Z2","Z3","Z4"),
                      treatment_name= "D",
                      P_hut_name= "P_hut",
                      bw=0.1,
                      beta0=beta0,
                      beta1=beta1,
                      data=RESULT_P_hut$Data,
                      l_eval=0.15,
                      u_eval=0.85,
                      kernel=locpol::gaussK,
                      covariate_value=covariate_value,
                      significance_level=0.05
)

head(RESULT_unif$Estimation)
RESULT_unif$Plot

```

## Note

-


## Reference

-  Tsuda, T, Jin, Y., & Okui, R. (2024+).
Uniform Confidence Band for Marginal Treatment Effect Function.
will be available on arXiv.
